Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-08-22 Paper/gammaRays.tex
Changed transient filtering out wording

Knowing the exposures, we can now use the method introduced in the appendix of \cite{Rubtsov:2011qq} to estimate the linear component of background from the data observed before the burst. We compute two background estimates: for low and high energy bands. Also, we have to filter out transient class photons completely, because their background appers to depend on the spacecraft position.

>>>>

Knowing the exposures, we can now use the method introduced in the appendix of \cite{Rubtsov:2011qq} to estimate the linear component of background from the data observed before the burst.
We compute two background estimates: for low and high energy bands.
Also, our method doesn't work for transient class photons, because their background appears to depend on the spacecraft position.
So we had to filter them out completely.
